---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# activAnalyzer.batch

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/pydemull/activAnalyzer.batch/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/pydemull/activAnalyzer.batch/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## General presentation
The goal of {activAnalyzer.batch} is to allow batch processing of accelerometer data files (.agd) using the functions from the {activAnalyzer} package. The core function of the package, `process_all_agd()`, implements parallel processing to inscrease the speed of the computations.

## Installation

The package is not published on CRAN. To install the package, you can use the following command line:

```{r, eval = FALSE}
devtools::install_github("pydemull/activAnalyzer.batch")
```

## Framework

### Set the directory structure

The working directory should have the following structure: 

**project**/  
&emsp;|_ **data**/  
&emsp;|&emsp;|_ **agd**/   
&emsp;|&emsp;|&emsp;|_ 001_...  
&emsp;|&emsp;|&emsp;|_ 002_...  
&emsp;|&emsp;|&emsp;|_ ...  
&emsp;|&emsp;|_ DATES.csv  
&emsp;|&emsp;|_ DEMO.csv  
&emsp;|_ config.csv  
        

In the `data/` folder, the .agd file names must start with the same number of digits (1, 2, 3,..). There are 3 digits in the example shown above.

The `DATES.csv` file should contain three columns (to ensure a correct structure of the file, the user can use the command `get_dates_template()` from the package to get a template of the file): 

  * A column for the IDs of the participants (named `id` for example).
  * A column for the date of the start of the measurement (named `start_date`).
  * A column for the date of the end of the measurement (named `end_date`).

The `DEMO.csv` file should contain at least four columns (to ensure a correct structure of the file, the user can use the command `get_demo_template()` from the package to get a template of the file):

  * A column for the IDs of the participants (named `id` for example).
  * A column for participant sex information (named `sex` for example).
  * A column for participant age in years (named `age` for example).
  * A column for participant weight in kg (named `weight` for example).

Importantly, the columns related to the participants IDs should have the same names across the different files.

The `config.csv` file should be generated using the following R command line: `get_config_file()`. Then, the user should update the values from the `USER_VALUE` column depending on their needs.

## Run batch analysis

To process all .agd files using a single function, run the following R commands:

```{r, eval = FALSE}
# Load package
library(activAnalyzer.batch)

# Process .agd files
df_pam <-
  process_all_agd(
    agd_dir = "data/agd/",
    config_path = "config.csv",
    demo_path = "data/DEMO.csv",
    dates_path = "data/DATES.csv",
    id_config = 3,
    content = "option_3"
  )
```

Please read the package documentation to get the details related to the function arguments.


